Manuscript

### 2018-01-05 manuscript.Rmd
Enable all three cities in Rmarkdown evaluation

@@

# variables
cities <- c("denver", "boston", "nyc")
```

@@

tract_shapes <- list(denver_tracts, boston_tracts, nyc_tracts)
park_shapes <- list(denver_parks, boston_parks, nyc_parks)
```

@@

#denver_tracts2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
plot(denver_tracts)

#denver_parks2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
plot(denver_parks)
```

Transform the attribute table into a tibble and select the relevant variables:
```{r transformdata}
#TODO: make sure all cities have the same data in the same names. It will save 
# us LOTS of time
# denver only, because the other cities have different variables
regression_data <-
  lapply(seq_along(1:1), function(i) {
    tbl_df(tract_shapes[[i]]@data) %>%
      mutate(
        Park_Percent = ifelse(is.na(Park_Percent), 0, Park_Percent),
        city = cities[i]
      )
  })
```

```{r}
denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = denver_plots)
```

@@

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  denver_tracts, denver_parks, betas = c(.00001, -5))
#regression_data[[2]]["park_ls"] <- calculate_park_logsums(
 # boston_tracts, boston_parks, betas = c(.00001, -30))
#regression_data[[3]]["park_ls"] <- calculate_park_logsums(
 # nyc_tracts, nyc_parks, betas = c(.00001, -5))
```

@@

  # TODO update when more cities are available
  models <- lapply(seq_along(1:1), function(city){
    errorsarlm(this_formula, data = regression_data[[city]],
               listw = list_ws[[city]], zero.policy = TRUE)
  })

  names(models) <- cities[1]
  return(models)
})

@@

  # TODO update when more cities are available
  models <- lapply(seq_along(1:1), function(city){
    lagsarlm(this_formula, data = regression_data[[city]],
             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed",
             tol.solve = 1e-16)
  })

  names(models) <- cities[1:3]
  return(models)
})

@@

  # TODO update when more cities are available
  models <- lapply(seq_along(1:1), function(city){
    lagsarlm(this_formula, data = regression_data[[city]],
             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed",
             tol.solve = 1e-16)
  })

  names(models) <- cities[1]
  return(models)
})

@@

mc_impacts <- lapply(park_sdm, function(dv){
  # TODO
  impacts <- lapply(seq_along(1:1), function(i) {
    impact_summary(summary(impacts(dv[[i]], tr = tr_mc[[i]], R = 500, empirical = TRUE)))
  })

  names(impacts) <- cities[1]

@@

Compare the models with `htmlreg()`. First the obesity models:
```{r denver_obesity_summary, results="asis", eval=FALSE}
denver_obesity_models <- list(
  #base_sem$OBESITY$denver, park_sem$OBESITY$denver,
  base_sdm$OBESITY$denver, park_sdm$OBESITY$denver,
  )

names(denver_obesity_models) <- paste(rep(c("SEM", "SDM"), each = 2), 
                                      rep(c("Base", "Parks")))

@@

Next, the physical activity models:
```{r denver_physact_summary, results="asis", eval=FALSE}
denver_physact_models <- list(
  base_sem$PhysAct$denver, park_sem$PhysAct$denver,
  base_sdm$PhysAct$denver, park_sdm$PhysAct$denver
)
names(denver_physact_models) <- paste(rep(c("SEM", "SDM"), each = 2),
                                      rep(c("Base", "Parks")))
htmlreg(denver_physact_models, caption = "Denver: Models of Physical Activity Participation")
```

>>>>

knitr::opts_chunk$set(cache = TRUE)

@@

# variables
cities <- c("boston", "denver", "nyc")
```

@@

tract_shapes <- list (boston_tracts, denver_tracts, nyc_tracts)
park_shapes <- list(boston_parks, denver_parks, nyc_parks)
```

@@

#denver_tracts2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
plot(boston_tracts)
#plot(denver_tracts)
#plot(nyc_tracts)

#denver_parks2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
plot(boston_parks)
#plot(denver_parks)
#plot(nyc_parks)
```

Transform the attribute table into a tibble and select the relevant variables:
```{r transformdata}
#TODO: make sure all cities have the same data in the same names. It will save 
# us LOTS of time
# denver only, because the other cities have different variables
regression_data <-
  lapply(seq_along(1:length(cities)), function(i) {
    tbl_df(tract_shapes[[i]]@data) %>%
      mutate(
        Park_Percent = ifelse(is.na(Park_Percent), 0, Park_Percent),
        city = cities[i]
      )
  })
```

```{r}
boston_plots <- spTransform(boston_tracts, CRSobj = CRS("+init=epsg:4326"))
denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
nyc_plots <- spTransform(nyc_tracts, CRSobj = CRS("+init=epsg:4326"))
library(leaflet)
leaflet() %>%
  addTiles() %>%
  #addPolygons(data = nyc_plots)
  #addPolygons(data = denver_plots)
  addPolygons(data = boston_plots)
```

@@

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
betas <- list(
  boston = c(0.00001, -30), 
  denver = c(0.00001, -15), 
  nyc = c(0.0001, -5)
)
for(i in 1:length(cities)){
  regression_data[[i]]["park_ls"] <- calculate_park_logsums(
    tract_shapes[[i]], park_shapes[[i]], betas = betas[[i]])
}
```

@@

  models <- lapply(seq_along(1:length(cities)), function(city){
    errorsarlm(this_formula, data = regression_data[[city]],
               listw = list_ws[[city]], zero.policy = TRUE)
  })

  names(models) <- cities
  return(models)
})

@@

  models <- lapply(seq_along(1:length(cities)), function(city){
    lagsarlm(this_formula, data = regression_data[[city]],
             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed",
             tol.solve = 1e-16)
  })

  names(models) <- cities
  return(models)
})

@@

  models <- lapply(seq_along(1:length(cities)), function(city){
    lagsarlm(this_formula, data = regression_data[[city]],
             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed",
             tol.solve = 1e-16)
  })

  names(models) <- cities
  return(models)
})

@@

mc_impacts <- lapply(park_sdm, function(dv){
  impacts <- lapply(seq_along(1:length(cities)), function(i) {
    impact_summary(summary(impacts(dv[[i]], tr = tr_mc[[i]], R = 500, empirical = TRUE)))
  })

  names(impacts) <- cities

@@

Compare the models with `htmlreg()`. First the obesity models:
```{r denver_obesity_summary, results="asis", eval=FALSE}
denver_obesity_models <- list(
  base_sdm$OBESITY$denver, park_sdm$OBESITY$denver
  )

names(denver_obesity_models) <- paste(rep(c("SDM"), each = 2), 
                                      rep(c("Base", "Parks")))

@@

Next, the physical activity models:
```{r denver_physact_summary, results="asis", eval=FALSE}
denver_physact_models <- list(
  base_sem$Phys_Act$denver, park_sem$Phys_Act$denver,
  base_sdm$Phys_Act$denver, park_sdm$Phys_Act$denver
)
names(denver_physact_models) <- paste(rep(c("SEM", "SDM"), each = 2),
                                      rep(c("Base", "Parks")))
screenreg(denver_physact_models, caption = "Denver: Models of Physical Activity Participation")
```
